\documentclass[12pt]{article}

\usepackage{marvosym}
\usepackage{multicol}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[T1]{fontenc}
\usepackage[dvipsnames]{xcolor}
\usepackage{geometry}
\geometry{letterpaper,left=0.3in,right=0.3in,top=0.4in,bottom=0.4in}

\newcommand{\sectionHeading}[1]{
\section*{\small{#1}}
\vspace{-8pt}
\hrule
\vspace{8pt}
}


\newcommand{\experienceSectionSubheading}[6]{
  \vspace{-1pt}
    \noindent \begin{tabular*}{1.01\linewidth}{l@{\extracolsep{\fill}}r}
      \small{\textbf{#1}} & \small{#2} \\
      \small{\textit{#3}} & \small{\textit{#4}} \\
      \small{\textit{#5}} & \small{\textit{#6}} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\experienceSectionSubheadingAlternate}[6]{
  \vspace{-1pt}
    \small{\textbf{Morgan Stanley \hfill New York, NY}} \\
    \small{\textit{#3} \hfill \textit{#4}} \\
    \small{\textit{#5} \hfill \textit{#6}} \\
    \vspace{-15pt}
}

\newcommand {\projectSectionSubheading}[3]{
    \noindent \small{\textbf{#1, }\textit{#2\hfill #3} }\vspace{-6pt}
}

\newcommand{\educationSectionSubheading}[3]{
    \vspace{-1pt}
    \noindent \begin{tabular*}{1.01\linewidth}{l@{\extracolsep{\fill}}r}
      \small{\textbf{#1, }\textit{#2}} & \small{\textit{#3}} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\sectionListStart}{\begin{itemize}[label={\small{\textbullet}},noitemsep]}

\newcommand{\sectionListEnd}{\end{itemize}}

\newcommand{\sectionListItem}[1]{\item \small{#1}}


\newcommand{\sectionListItemWithDate}[2]{\item \small{#1 \hfill \textit{#2}} \\\vspace{-10pt}}

%RESUME STARTS HERE -------------------------------------------->

%%%%%%%%%%%%%%%%%%%%%% INTRO AND CONTACT INFORMATION %%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\begin{center}
\LARGE{\textbf{AADARSH KENIA}}\\
\vspace{4pt}
\small{\Letter \hspace{1mm}akenia@cs.stonybrook.edu} | \Telefon \hspace{1mm}631 974 8070
% \small{\Letter \hspace{1mm}akenia@cs.stonybrook.edu} | \Telefon \hspace{1mm}631 974 8070
% \small{\Telefon \hspace{1mm}631 974 8070}\\
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%% WORK EXPERIENCE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\sectionHeading{WORK EXPERIENCE}
\experienceSectionSubheadingAlternate
{Morgan Stanley}{New York, NY}
{Technology Associate}{Nov '16 - Present}
{Technology Analyst}{Aug '16 - Nov '16}
\sectionListStart
    \sectionListItem
        Designed and implemented a RESTful middleware through API-first design principles(Swagger) that serves firm's online portal and significantly improves document collaboration experience for clients.
    % \sectionListItem
    %     Implemented a metadata routing module as part of an in-house document management platform that is set to replace a legacy system and help save \$1.7M annually.
    \sectionListItem
        Built a metadata routing component as part of an in-house document management platform that is set to replace a legacy system and cut costs by \$1.7M annually.
    \sectionListItem
        Reduced interfacing limitations of workflow systems by implementing a gateway component that exposes REST APIs  and enables pub-sub capabilities to message queues, refactored the gateway and increased unit test coverage from 50\% to 70\%. 
    \sectionListItem
        Ensured stability of a back-end system by throttling number of requests sent per second, implemented periodic retries of failed messages to enable automated recovery.
    \sectionListItem
        Promoted the concept of API-first design within the team for good software development practices.
\sectionListEnd


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% EDUCATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\sectionHeading{EDUCATION}
\educationSectionSubheading
{Stony Brook  University}{M.S Computer Science, GPA: 3.56/4}{Aug '14 - May '16}
\sectionListStart
    \sectionListItem
        Coursework: Operating Systems, Algorithms, Asynchronous Systems, Computational Biology, Parallel Computing. 
\sectionListEnd

\educationSectionSubheading
{University of Mumbai}{B.E Computer Science, GPA: 4/4 (Aggr. 75\%)}{Sep '10 - May '14}


%%%%%%%%%%%%%%%%%%%%%%%%%% PROJECTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\sectionHeading{PROJECTS}
\projectSectionSubheading{GDFS}{Hobby project}{Ongoing}
\sectionListStart
    \sectionListItem
        Wrote a python implementation of file system in user space (FUSE), that automatically backs up files from local file system to Google Drive based on callbacks. Python, Drive SDK, FUSE lib.
\sectionListEnd

\projectSectionSubheading{Unify}{Hobby project}{2016}
\sectionListStart
    \sectionListItem
        Android app that simplifies task management by combining events from Google Calendar and Evernote. Android, Calendar \& Evernote APIs.
\sectionListEnd

\projectSectionSubheading{SBUnix Operation System}{Stony Brook University}{2015}
\sectionListStart
    \sectionListItem
        Built an X86\_64 pre-emptive OS with support for memory management, process scheduling, context switching and unix like shell. Implemented all sys calls from scratch. C, ASM, QEMU emulator.
        

\sectionListEnd

%%%%%%%%%%%%%%%%%%%%%%%%%% LEADERSHIP AND AWARDS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\sectionHeading{LEADERSHIP AND AWARDS}
\sectionListStart
    \sectionListItemWithDate
        {Intern Mentorship - Mentored a summer intern at Morgan Stanley by providing guidance on internal technologies, firm values, project blockers, etc. to help them have a fulfilling internship experience.}{2017} 
    \sectionListItemWithDate
        {Awarded `Rookie of the year, Field \& Client Tech' - one of the top performing employees at Morgan Stanley.}{2017}
    \sectionListItemWithDate
        {Volunteer, Stony Brook Child Care Services - Assist in overall personality development of children by engaging their involvement in various fun learning events.}{2015}
\sectionListEnd

%%%%%%%%%%%%%%%%%%%%%%%%%% LANGUAGES AND TECHNOLOGIES  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\sectionHeading{LANGUAGES AND TECHNOLOGIES}
\sectionListStart
    \sectionListItem
        Java (Proficient), Spring, Google Protocol Buffers, SQL, Git, IntelliJ IDEA.
    \sectionListItem
        C, C++, JavaScript, Python, Android. 
\sectionListEnd

%RESUME ENDS HERE -------------------------------------------->
\end{document}